Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
minor fix
fix: typos

\begin{abstract}
%\boldmath
Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.
We used the projects stored in the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. In particular, we analyzed every project version of the repository by using a
popular static analysis tool. Then by taking advantage of
the repository's features (multiple versions for every project, dependencies) we studied
the evolution of security bugs through time, their persistence and their relationship with a) the
size of the corresponding version and b) other bug categories. Our findings
indicate that there is no simple relationship between the number of
security bugs and project evolution.
In addition, they are not eliminated in a way that is particularly
different from the other bugs. Their relation with
size appears to be different from the other categories. Finally, even if bugs
seem to flock together, severe security bugs
seem to be unassociated with other categories.
\end{abstract}

@@

The goal of our experiment was to retrieve all the bugs that FindBugs reports,
for all the project versions existing on the Maven repository.
The experiment involved four entities:
a number of {\it workers} (a custom Python script), a {\it task queue}
mechanism (Rabbit{\sc mq} - version 3.0.1),\footnote{\url{http://www.rabbitmq.com/}}
a {\it data repository} (Mongo{\sc db} - version 2.2),\footnote{\url{http://www.mongodb.org/}}
and the {\it code repository}, which in our case it was
the public Maven repository.

@@

In this work we analyzed a large software repository to examine the
behavior of security bugs. Specifically, we analyzed more than 260GB
of interdependent project versions to see how security bugs evolve
over time, their persistence, their relation with other bug
categories, and their relationship with size in terms of bytecode.

@@

Contrary to the approaches that examine all versions
formed after every change that has been commited to the repository,
our observations are made from a different perspective.
The versions examined in this work were actual releases
of the projects. As a result we do not have an indication of how many changes
have been made between the releases.
In essence, these {\sc jar}s were the ones that were or still are,
out there in the wild, being used either as applications,
or dependencies of others.

>>>>

\begin{abstract}
%\boldmath
Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.
We used the projects stored in the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. In particular, we analyzed every project version of the repository by using a
popular static analysis tool. Then by taking advantage of
the repository's features (multiple versions for every project, dependencies) we studied
the evolution of security bugs through time, their persistence and their relationship with a) the
size of the corresponding version and b) other bug categories. Our findings
indicate that there is no simple relationship between the number of
security bugs and project evolution.
In addition, they are not eliminated in a way that is particularly
different from the other bugs. Their relation with
size appears to be different from the other categories. Finally, even if bugs
seem to flock together, severe security bugs
seem to be dissociated with other categories.
\end{abstract}

@@

The goal of our experiment was to retrieve all the bugs that FindBugs reports,
from all the project versions existing on the Maven repository.
The experiment involved four entities:
a number of {\it workers} (a custom Python script), a {\it task queue}
mechanism (Rabbit{\sc mq} - version 3.0.1),\footnote{\url{http://www.rabbitmq.com/}}
a {\it data repository} (Mongo{\sc db} - version 2.2),\footnote{\url{http://www.mongodb.org/}}
and the {\it code repository}, which in our case it was
the public Maven repository.

@@

In this work we analyzed a large software repository to examine the
behavior of security bugs. Specifically, we analysed more than 260GB
of interdependent project versions to see how security bugs evolve
over time, their persistence, their relation with other bug
categories, and their relationship with size in terms of bytecode.

@@

Contrary to the approaches that examine all versions
formed after every change that has been committed to the repository,
our observations are made from a different perspective.
The versions examined in this work were actual releases
of the projects. As a result we do not have an indication of how many changes
have been made between the releases.
In essence, these {\sc jar}s were the ones that were or still are,
out there in the wild, being used either as applications,
or dependencies of others.
